|

### 2024-11-15 output/seminar-slideshow.qmd
Add labels to all contour plots in difficulty plot

contour_plot +
  geom_segment(
    data    = mirt_item_spikes,
    mapping = aes(
      trait_1_start, trait_2_start,
      xend = trait_1_end,
      yend = trait_2_end
    ),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color = PALETTE_BLUE["light"]
  ) +
  geom_point(
    data = mirt_item_coords,
    mapping = aes(origin_1, origin_2),
    inherit.aes = FALSE,
    size = I(4)
  ) +
  scale_x_continuous(
    breaks       = -1:1,
    minor_breaks = NULL,
    limits       = c(-1.5, 1.5),
    expand       = expansion(),
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~2~", labels = NULL)
  ) +
  scale_y_continuous(
    breaks       = -1:1,
    minor_breaks = NULL,
    limits       = c(-1.5, 1.5),
    expand       = expansion(),
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~1~", labels = NULL)
  ) +
  annotate(
    geom = "richtext",
    x = 0.16, y = 0.15,
    label = "*MID~i~*",
    size = 6,
    angle = mirt_item_params |> pull(deg_1),
    label.colour  = NA,
    fill = NA
  )
```
:::

>>>>

mirt_item_probs |>
  ggplot(mapping = aes(trait_1, trait_2, z = prob, label = after_stat(level))) +
  geom_vline(xintercept = 0, linewidth = GRID_WIDTH) +
  geom_hline(yintercept = 0, linewidth = GRID_WIDTH) +
  geom_contour2(
    color = F1_COLOR,
    linewidth = LINE_WIDTH,
    skip = 0,
    breaks = 1:9 / 10,
    label.placer = label_placer_fraction(frac = .90, rot_adjuster = 0)
  ) +
  geom_segment(
    data    = mirt_item_spikes,
    mapping = aes(
      trait_1_start, trait_2_start,
      xend = trait_1_end,
      yend = trait_2_end
    ),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color = PALETTE_BLUE["light"]
  ) +
  geom_point(
    data = mirt_item_coords,
    mapping = aes(origin_1, origin_2),
    inherit.aes = FALSE,
    size = I(4)
  ) +
  scale_x_continuous(
    breaks       = -1:1,
    minor_breaks = NULL,
    limits       = c(-1.5, 1.5),
    expand       = expansion(),
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~2~", labels = NULL)
  ) +
  scale_y_continuous(
    breaks       = -1:1,
    minor_breaks = NULL,
    limits       = c(-1.5, 1.5),
    expand       = expansion(),
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~1~", labels = NULL)
  ) +
  annotate(
    geom = "richtext",
    x = 0.16, y = 0.15,
    label = "*MID~i~*",
    size = 6,
    angle = mirt_item_params |> pull(deg_1),
    label.colour  = NA,
    fill = NA
  ) +
  coord_fixed() +
  theme(
    axis.ticks       = element_blank(),
    axis.line        = element_blank(),
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH)
  )
```
:::
